Reanalysis Step 5: Sensitivity Analysis with E-values

### 2025-08-20 reanalysis-5-sensitivity.qmd
file name

# Load results from previous steps
ps_results <- readRDS(file.path(reanalysis_data_dir, "ps_results_twang.rds"))
pooled_results <- readRDS(file.path(reanalysis_data_dir, "pooled_results.rds"))
subgroup_effects <- readRDS(file.path(reanalysis_data_dir, "subgroup_effects.rds"))
```

>>>>

# Load results from previous steps
ps_results <- readRDS(file.path(reanalysis_data_dir, "ps_results_twang.rds"))

# Load outcome analysis results (from step 4)
outcome_results <- readRDS(file.path(reanalysis_data_dir, "outcome_analysis_results.rds"))
pooled_results <- outcome_results$pooled_coefficients
subgroup_effects <- outcome_results$subgroup_effects
```
